Assessing Racial Bias in Arrest and Booking Practices in Toronto from 2020-2021

### 2024-12-04 paper/paper.qmd
Adding references

@@

ggplot(table3_long, aes(x = perceived_race, y = value, fill = factor(age_group))) +
  geom_bar(stat = "identity") +
  facet_wrap(~ year, scales = "free_y") +
  labs(x = "Perceived Race",
       y = "Number of People",
       fill = "Year") +
  theme_minimal() +
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

@@

[@fig-ppc] shows a posterior predictive check was performed. It illustrates a comparison between posterior distribution simulations and the actual probability of experiencing a custody arrest

>>>>

ggplot(table3_long, aes(x = perceived_race, y = value, fill = factor(age_group))) +
  geom_bar(stat = "identity") +
  facet_wrap(~ year, scales = "free_y") +
  labs(x = "Perceived Race",
       y = "Number of People",
       fill = "Year") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set3") +
  theme(legend.position = "bottom") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

@@

The `rstanarm` package [@citerstanarm] and the R programming language [@citeR] were employed in order to run this model.

The `modelsummary` package [@citeModelsummary] was used to create [@tbl-model], [@fig-credibility-intervals-all], and [@fig-credibility-intervals-several.]

@@

Using code adapted from [@citeAlexander] a posterior predictive check was performed. [@fig-ppc] illustrates a comparison between posterior distribution simulations and the actual probability of experiencing a custody arrest
